---
title: "Getting Started with lwPackageHelpR"
# author: "John Minter"
date: "Last updated: 2019-04-15"
output:
  rmarkdown::html_vignette:
    number_sections: true
    toc: true
    toc_depth: 2
vignette: >
  %\VignetteIndexEntry{Getting Started with lwPackageHelpR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
```
# Introduction

`lwPackageHelpR` is a light weight R package install and update manager.

# Key Functions

There are two key functions:

1. `install_new(pkg, repo = "http://cran.revolutionanalytics.com/", libPath = .libPaths()[1]))`

2.  `install_new_github(pkg, repo, libPath)`

# Examples

## Install a new package

This function checks to see if the package is installed. If not,
it will install the package. Use it like this:

```{r install_dt}
if( Sys.info()['sysname'] == "Windows"){
	
	Sys.setenv(JAVA_HOME="")
	print("unset JAVA_HOME for Windows")
}

library(lwPackageHelperR)
install_new('devtools', .libPaths()[1])

```

## Install a new package from github

Here we install the development version of Yihui Xie's
`xaringan` package from github.

``````{r install_xa_gt}
if( Sys.info()['sysname'] == "Windows"){
	
	Sys.setenv(JAVA_HOME="")
	print("unset JAVA_HOME for Windows")
}

install_new_github('xaringan','yihui',.libPaths()[1])

```
